Deciding to Disclose

### 2015-01-08 Background.tex
Minor tweaks

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

@@

While game theory addresses rational strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

@@

As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Burke1996,Oliver2003}). Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option. While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.

>>>>

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

@@

While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

@@

As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support from \citet{Burke1996} and \citet{Oliver2003}). Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option. While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.

### 2015-01-08 Conclusion.tex
Minor tweaks

In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about particular women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

>>>>

In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

### 2015-01-08 Introduction.tex
Minor tweaks

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may well map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem. In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.

>>>>

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem. In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.

### 2015-01-08 Model.tex
More explanation for simplified tree
Minor tweaks

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Arrows correspond to two moves by nature, followed by women, and midwives respectively. Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, with $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using the rules described in section \ref{sub:the_agents}.

@@

\[
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\]

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate more than two `prospects'.\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

>>>>

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Arrows correspond to two moves by nature, followed by women, and midwives respectively. Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types. For midwives, referral is shown by a heavier arrow. Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions - 
\begin{equation}
u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}},
\end{equation} 
\begin{equation}
u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.

@@

\begin{equation}
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate the `prospects'\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} of more than two actions. \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
